\documentclass[margin,line]{resume}

\begin{document}
\name{\Large{Feifei Hang}\vspace{0.3cm}}
\begin{resume}
    %--------------------------
    % Contact information & personal details
    \section{\mysidestyle Personal\\Details}

    Flat 113, Horniman House    \hfill Tel: (0044) 07407031512         \vspace{0mm}\\\vspace{0mm}%
    66 Grafton Street           \hfill E-mail: l.daniel.hung@gmail.com \vspace{0mm}\\\vspace{0mm}%
    Manchester, UK              \hfill Website: feifeihang.blog.com    \vspace{0mm}\\\vspace{-4.5mm}%
    M13 9NT                     \vspace{1em}


    %---------------------------
    % Education
    \section{\mysidestyle Education}
    \textbf{University of Manchester}, United Kingdom \vspace{2mm}\\\vspace{1mm}%
    \textsl{Doctor of Philosophy} \hfill \textbf{2012 -- present} \vspace{-1.5mm}

    \textbf{University of Leicester}, United Kingdom \vspace{2mm}\\\vspace{1mm}%
    \textsl{Master of Science with Distinction} in Advanced Software Engineering \hfill \textbf{2010 -- 2011}\\\vspace{-1mm}%
    \textsl{Modules included:}\\\vspace{-3mm}
    \begin{list2}
    \item Advanced System Design                      \hfill  \textbf{Distinction}
    \item Service-Oriented Architectures              \hfill  \textbf{Distinction}
    \item Software Re-engineering                     \hfill  \textbf{Distinction}
    \item Distributed Systems and Applications        \hfill  \textbf{Distinction}
    \item Personal \& Group Skills                    \hfill  \textbf{Distinction}
    \item Generative Development                      \hfill  \textbf{Merit}
    \item Advanced Web Technology                     \hfill  \textbf{Pass}
    \item Software Quality Assurance and Measurement  \hfill  \textbf{Pass}
    \end{list2}
    \textsl{MSc Dissertation:} A Graphical Programming Language for the Android Platform \vspace{-1.5mm}

    \textbf{James Cook University}, Australia \vspace{2mm}\\\vspace{1mm}%
    \textsl{Bachelor of Information Technology} \hfill \textbf{2006 -- 2010}\\\vspace{-3mm}


    %-----------------------------
    % Computing skills
    \section{\mysidestyle Computing\\Skills}

    \textbf{Applications \& Packages:} \vspace{2mm}\\\vspace{1mm}%
    Microsoft Office Suite, LibreOffice (OpenOffice.org) Suite, Dreamweaver, Adobe Photoshop, Eclipse, NetBeans, Microsoft Visual Studio, several e-mail packages, and etc..

    \textbf{Languages:} \vspace{2mm}\\\vspace{1mm}%
    Java, C, C++, C\#, Python, SQL, \LaTeX{}, and etc..

    \textbf{Operating Systems:} \vspace{2mm}\\\vspace{1mm}%
    Unix, Linux, Microsoft Windows, Mac OS X


    %-----------------------------
    % Honour & Awards
    \section{\mysidestyle Honour \&\\Awards}

    \textbf{Top one in Java module} \hfill \textbf{2008}\vspace{2mm}\\\vspace{1mm}%
    Ranked the first in the module of Object-Oriented Programming in whole campus.

    \textbf{Student of the Year in China's Campus} \hfill \textbf{2006}\vspace{2mm}\\\vspace{1mm}%
    Finished the first year study with outstanding achievements.


    %------------------------------
    % Experience
    \section{\mysidestyle Employment \&\\Experience}

    \textbf{University of Manchester}, United Kingdom           \vspace{2mm}\\\vspace{1mm}%
    \textsl{Teaching Assistant} \hfill \textbf{2012 -- present} \vspace{2mm}\\\vspace{1mm}%
    Working as a teaching assistant to demonstrate lab sessions in School of Computer Science at the University of Manchester.

    \textbf{Everthriving Investment Group}, Beijing, China              \vspace{2mm}\\\vspace{1mm}%
    \textsl{Systems and Software Engineer} \hfill \textbf{2009 -- 2010} \vspace{2mm}\\\vspace{1mm}%
    Worked as part of the department of ERP systems to design, implement, and maintain the ERP systems and databases that we produced for Everthriving Investment Group and its clients. Since I was the technical lead in the team, I also focused on the quality assurance and encouraged the team to follow the Agile Methodology.

    After the one-year period development, we not only implemented the functionalities that required by our clients, but also built several add-value components. Once our final code and runnable system were released to our clients, the customers showed their great satisfies and promoted our system in several departments in their companies.

    \textbf{James Cook University}, China's Campus           \vspace{2mm}\\\vspace{1mm}%
    \textsl{Teaching Assistant} \hfill \textbf{2007 -- 2008} \vspace{2mm}\\\vspace{1mm}%
    I was in charge of helping the tutors to answer questions from students who were learning C/C++ and Java. Additionally, my duties also involved holding and teaching in workshops and surgeries, which aimed to assist students to reduce the difficulties in overcoming their problems in C/C++ and Java.

    Both teachers and students are quite happy with my services and assistants. Most of the students have improved their programming skills with my help.
    
    
    %---------------------------------
    % Major projects
    \section{\mysidestyle Major\\Projects}

    \textbf{OpenBasement Database Management System} \hfill \textbf{2010 -- present}\vspace{2mm}\\\vspace{1mm}%
    I am recently involved in OpenBasement project, which is based on the close-source project “Basement” I did in 2009, in order to produce a free and open-source database management system to the public.

    Project home: \textsl{http://code.google.com/p/basement-dbms/}

    \textbf{Atom Scripting Language} \hfill \textbf{2009 -- 2010}\vspace{2mm}\\\vspace{1mm}%
    A light-weight and open-source scripting language project which aims at proposing a fast and simple language.

    Project home: \textsl{http://code.google.com/p/atom-scripting-language/}

    \textbf{GNUer Lib Project} \hfill \textbf{2009 -- 2010}\vspace{2mm}\\\vspace{1mm}%
    A library, which involves several useful methods and data types, helps people program in C.

    Project home: \textsl{http://code.google.com/p/gnuer-lib/}

    \textbf{Cloudy Venus Project} \hfill \textbf{2009}\vspace{2mm}\\\vspace{1mm}%
    A highly integrated alternative to Microsoft Windows Explorer for academic uses.

    Project home: \textsl{http://code.google.com/p/cloudy-venus/}

    %----------------------------------
    % Interests
    \section{\mysidestyle Interests}

    Listening music, watching movies, karaoke, swimming, jogging, mountain climbing, scuba diving

\end{resume}
\end{document}

